---
output: github_document
---

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/fastDummies)](https://cran.r-project.org/package=fastDummies) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/jacobkap/fastDummies?branch=master&svg=true)](https://ci.appveyor.com/project/jacobkap/fastDummies) 
[![Build Status](https://travis-ci.org/jacobkap/fastDummies.svg?branch=master)](https://travis-ci.org/jacobkap/fastDummies)

## Overview

The goal of fastDummies is to quickly create dummy variables (columns) and dummy rows. Creating dummy variables is possible through base R or other packages, but this package is much faster than those methods. 

## Installation
```{r, eval = FALSE}
To install this package, use the code
install.packages("fastDummies")


# The development version is available on Github.
# install.packages("devtools")
devtools::install_github("jacobkap/fastDummies")
```

## Usage

```{r}
library(fastDummies)
```

There are two functions in this package:

* `dummy_cols()` lets you make dummy variables (`dummy_columns()` is a clone of `dummy_cols()`)    
* `dummy_rows()` which lets you make dummy rows.
